### 2022-03-27 msred-geometry.tex
Finished section 3 with Casey's contribution.

%- Packages ----------------------------------------------------------------------------------------------
\usepackage{custom-style}
\usetikzlibrary{positioning}
\usepackage{multicol}
\usepackage{bbold}

@@

 \item Notice that the antisymmetrization of $\llbracket \cdot, \cdot \rrbracket$ equates $\lbrace \cdot,\cdot \rbrace$ modulo homotopy:
 \begin{align*}
  \llbracket \sigma_1,\sigma_2 \rrbracket  \circ 	\mathcal{A}
  =&~
  \frac{\mathcal{L}_{\vHam_1}\sigma_2 - \mathcal{L}_{\vHam_2}\sigma_1}{2} 
  \\
  =&~ 
  \frac{1}{2}( d (\iota_{\vHam_1}{\sigma_2} - \iota_{\vHam_2}{\sigma_1} )
  +\frac{1}{2}(-\iota_{\vHam_1}\iota_{\vHam_2}\omega + \iota_{\vHam_2}\iota_{\vHam_1}\omega) 
  \\
  =&~
  \lbrace \sigma_1, \sigma_2 \rbrace + d \circ \langle\sigma_1,\sigma_2\rangle_-
  \\
  =&~
  [\sigma_1,\sigma_2]_\omega
 \end{align*}
 where the last bracket is given by the Higher Courant bracket.
}
%-------------------------------------------------------------------------------------------------------------------------------------------------

>>>>

%- Packages ----------------------------------------------------------------------------------------------
\usepackage{custom-style}
\usepackage{math}
\usetikzlibrary{positioning}
\usepackage{multicol}
\usepackage{bbold}

@@

 \item Notice that the antisymmetrization of $\llbracket \cdot, \cdot \rrbracket$ equates $\lbrace \cdot,\cdot \rbrace$ modulo homotopy:
 \begin{align*}
  \llbracket \sigma_1,\sigma_2 \rrbracket  \circ 	\mathcal{A}
  =&~
  \frac{\mathcal{L}_{\vHam_1}\sigma_2 - \mathcal{L}_{\vHam_2}\sigma_1}{2} 
  \\
  =&~ 
  \frac{1}{2}( d (\iota_{\vHam_1}{\sigma_2} - \iota_{\vHam_2}{\sigma_1} )
  +\frac{1}{2}(-\iota_{\vHam_1}\iota_{\vHam_2}\omega + \iota_{\vHam_2}\iota_{\vHam_1}\omega) 
  \\
  =&~
  \lbrace \sigma_1, \sigma_2 \rbrace + d \circ \langle\sigma_1,\sigma_2\rangle_-
  \\
  =&~
  [\sigma_1,\sigma_2]_\omega
 \end{align*}
 where the last bracket is given by the Higher Courant bracket.
 \item Take away: Two brackets on $\Omega_H^{k-1}(M)$, ${\color{red}\llbracket\alpha,\beta\rrbracket = \mathcal{L}_{X_\alpha} \beta}$ and ${\color{green}\{\alpha,\beta\}=\iota_{X_\alpha}\d\beta}$,
	Equal up to a coboundary: ${\color{red}\mathcal{L}_{X_\alpha}\beta} = {\color{green}\iota_{X_\alpha}\d\beta} + \d\hspace{1pt}\iota_{X_\alpha}\beta$
}
%-------------------------------------------------------------------------------------------------------------------------------------------------
